---
title: "EULAR GROUP"
author: "Pfizer"
date: 'June 12th to June 16th'
output:
 
  html_document:
    css: FORMATO.css
    fig_width: 8
    fig_height: 8
    highlight: espresso
    theme: cosmo
    toc: yes
    toc_float: yes
---

<script> 
    $(document).ready(function() { 
    $head = $('#header'); 
    $head.prepend('<A href = https://www.cuttingedge-events.com><img src ="LOGO.png" width="150" align="right"></A>') 
    }); 
</script> 


```{r echo=FALSE, message=FALSE,warning=FALSE}
library(readxl)
library(shiny)
library(dplyr)
library(knitr)
```


## SUGGESTED RESTAURANTS{.tabset .tabset-fade .tabset-pills}

### **Wednesday the 12th**

**La Malontina**

We propose you "La Malontina" restaurant for the 12th dinner. 

La Malontina is a restaurant focused on traditional spanish cuisine with a creative touch. Its decoration is simply but fine. It combines the red walls with a really soft light that creates a really good atmosphere.

Its basic menu is about dishes to share. 7 different tasty dishes to discover a creative spanish cuisine. The menu also includes drink package but not coffee.

&nbsp;

<img src = "https://cdn.restaurantes.com/static/img/restaurants/288/28852/28852_1176.gl.jpg" width="720">

### **Thursday the 13th**

**Los Galayos**

The Restaurant Los Galayos is located in *La Plaza Mayor* in the *Austrias Neighbourhood*. Los Galayos has seen pass away the time; if the walls speak they would explain how was Madrid more than one hundred years ago, in the ages when La Puerta del Sol and La Plaza Mayor were the centre of gatherings and kingdom´s special Ceremonies. Los galayos has different dinning rooms, every dinning room has it own special environment and they have been decorated to offer all possible new sensations for visitors to taste a great typical traditional Spanish cuisine.

The Spanish cuisine that they offer now is more elaborated, due to the interest of the proprietors in the investigation of the new current kitchen offering a wide variety inside its menu.

Its basic menu includes 3 starters to share, a main dish to choose, a dessert and coffee. Drink package is included (wine and water)

&nbsp;

<img src = "https://www.losgalayos.net/media/6788/terraza-losgalayos-17_Grande.jpg" width="720">

&nbsp;

<img src = "http://blog.losgalayos.net/wp-content/uploads/2013/12/Salon-Duque2.jpg?w=640" width="720">

### **Friday the 14th**

**O Pulpo**

O Pulpo is a donwtown's restaurant. 

This restaurant has an amazing spanish atmosphere. The decoration is about warm colors with tipical spanish trimmings. 
O Pulpo offers a Galician cuisine and all their products are a first quality, choosen daily by the owner.

Its basic menu includes 4 starters to share, a main dish to choose and a dessert to choose. Drink package is included.

&nbsp;

<img src = "https://cdn.restaurantes.com/static/img/restaurants/805/8053/8053_89.gl.jpg" width="720">

&nbsp;

<img src = "https://cdn.restaurantes.com/static/img/restaurants/805/8053/8053_7916.gl.jpg" width="720">

### **Saturday the 15th**

**Ana La Santa**

Ana La Santa is located at Plaza Santa Ana, at Madrid's downtown. Is about an idilic restaurant specialized in Mediterranean and spanish cuisine. 

The gastronomic proposal of the restaurant is based on the preparation of excellent Spanish and Mediterranean recipes, made with the best ingredients from the best local markets.

The basic menu includes 4 starters to share, a main dish to choose and a dessert to choose. Drink package included (also coffee)

<img src = "https://cdn.restaurantes.com/static/img/restaurants/941/94101/94101_6242.gl.jpg" width="720">

&nbsp;

<img src = "http://www.buscorestaurantes.com/files/images/Ana-La-Santa-130085.jpg" width="720">


## PROGRAMME

### **Programme Overview and timeline**

```{r echo=FALSE, message=FALSE,warning=FALSE}
library(timevis)
library(dplyr)
library(readxl)

timeline <- read_excel("timeline.xlsx", sheet = "Sheet1", 
    col_types = c("date", 
        "text", "text", "numeric", "text", 
        "text"))

data <- data.frame( id = 1:length(timeline$start),
                    start = as.POSIXlt(timeline$start),
                    content = timeline$content,
                    group = timeline$group,
                    type = "box",
                    style = "background-color:#FF9933;")

groups = data.frame(id = 1:4, content = c("Morning", "Lunch", "Afternoon", "Diner"))

tl <- timevis(data, groups, showZoom = TRUE, zoomFactor = 0.2, fit = TRUE, width = '100%', height = 300)

tl %>% setOptions(list(orientation = "top", align = "left"))

```

### **MAP**

```{r echo=FALSE, warning=FALSE, message=FALSE}

library(leaflet)
library(stringr)
library(ggmap)
library(readxl)
library(dplyr)
library(leaflet.extras)
library(shiny)

coordinates <- read_excel("timeline.xlsx", 
    sheet = "Sheet3", col_types = c("text", 
        "text", "numeric", "numeric", "text", 
        "text"))

coordinates$Category <- factor(coordinates$Category)

m <- coordinates %>% 
  leaflet(options = leafletOptions(dragging = TRUE,
  minZoom = 14, maxZoom = 18)) %>% 
  addProviderTiles("Esri") %>% 
  setView(lng = 2.1687300, lat = 41.3863900, zoom = 14) 

pal <- colorFactor(palette = c("red","blue"),
      levels = coordinates$Category)

m %>% clearBounds() %>% 
  addCircleMarkers(radius = 5, color = ~pal(Category)) %>% 
  addPopups(popup = paste0("<b>",coordinates$Location,"</b>")) %>% 
  addLegend(position = "bottomright", pal = pal, 
  values = coordinates$Category) %>% addResetMapButton()

```


*****
## BUDGET

```{r echo=FALSE, message=FALSE,warning=FALSE}

library(readxl)
library(dplyr)
library(knitr)
library(kableExtra)
library(DT)

budget <- read_excel("timeline.xlsx", sheet = "Sheet2", 
    col_types = c("date", "text", "text", 
        "numeric", "text", "numeric", "numeric"))
budget$DATE <- as.Date(budget$DATE)

DT::datatable(budget, extensions = "Buttons",rownames = FALSE, options = list(paging= FALSE,
initComplete = JS("
    function(settings, json) {
      $(this.api().table().header()).css({
        'background-color': '#ee7600 ',
        'color': '#fff'
      });
    }"),
dom ='Bfrtip', buttons = c('copy','print'),                           pageLength = nrow(budget),autoWidth = TRUE)) %>% 
   formatDate('DATE') %>% 
  formatCurrency(6:7,'\U20AC')


```

### Terms & Conditions

  *Rates valid for 2019.
  
  *Cutting Edge Events management fee including in the detailed rates
  
  *VAT included. 
  
  *No reservation has been done. Availability upon request.
  
*****

